%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[16pt, a4paper]{awesome-cv}

%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

%%% Configure a directory location for sections
\newcommand*{\sectiondir}{cv/}

%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete,
% awesome-darknight
%% Color for highlight
% Define your custom color if you don't like awesome colors
\colorlet{awesome}{awesome-red}
 
%\definecolor{awesome}{HTML}{CA63A8}
%% Colors for text
%\definecolor{darktext}{HTML}{414141}
\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

%%% Override a separator for social informations in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Personal Data
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Essentials
\name{Andrei}{ Tumbar}
\address{Rochester Institute of Technology}
\mobile{(+1) 607-379-0960} 
%%% Social
\email{at1777@rit.edu}
\github{kronos3}
%\linkedin{posquit0}
%%% Optionals
\position{BSeng Candidate{\enskip\cdotp\enskip}Computer Engineering}
%\quote{``Make the change that you want to see in the world."}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Letter Data (Cover Letter)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipient
  { SAAB }
  {Syracuse, NY}
\letterdate{\today}
\lettertitle{The position as Test Engineer Co-Op/Intern}
\letteropening{Dear Hiring Manager,}
\letterclosing{Sincerely,}
%\letterenclosure[Attached]{Curriculum Vitae}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Content
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Make a footer for CV with three arguments(<left>, <center>, <right>)
\makecvfooter
  {\today }
  {Andrei Tumbar~~~·~~~Cover Letter}
  {}

\begin{document}
%%% Make a header for CV using personal data
\makecvheader
%%% Make a title for Cover Letter using letter data
%\makelettertitle
%%% Write content for your cover letter
\vspace{3cm}
\begin{cvletter}
\cvparagraph{Dear Hiring Management,}

\par I am a Computer Engineering student at Rochester Institute of Technology looking for a summer co-op/internship. I came to learn about SAAB at the RIT career fair on 2/26/20 and read more about the work you do here. Because of my extensive Linux knowledge as well as experience in C, Python, and Java I think I am a strong candidate for the Software Engineering position. I have worked on a long-term project where I am looking to make Gentoo Linux a more mainstream/viable operating system. Through this project, I have been exposed to most of the Linux subsystems and understand its inner workings. Beyond Linux, I have worked with network programming, multi-threaded scheduling, tree-recursion, advanced data-types as well as web-frameworks. My Github (github.com/Kronos3) has over 20 repositories of projects I have worked on over the years from robot control to website design and everything in between.

\par I think that all of these skills described make me a perfect candidate for an internship position at SAAB. While talking with Diego Gomes during the RIT career fair, I learned about the sort of work I would be doing here. Having experience in a wide variety of areas as well as being able to learn new things independently will be useful as a software engineer. Thank you for considering my application, I look forward to hearing from you.


\end{cvletter}

%%% Make a closing for Cover Letter using letter data
\makeletterclosing

\end{document}
