% -- Encoding UTF-8 without BOM
% -- XeLaTeX => PDF (BIBER)

\documentclass[]{alternate} 

\sethyphenation[variant=british]{english}{} % Add words between the {} to avoid them to be cut 
\usepackage{hyperref}% http://ctan.org/pkg/hyperref
\hypersetup{
  colorlinks=true,
  linkcolor=blue!50!red,
  urlcolor=green!70!black
}
\begin{document}

\header{Andrei}{ Tumbar}

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION  -- In the aside, each new line forces a line break
%----------------------------------------------------------------------------------------

\border{}
\bordersecond{}

\begin{aside}
%
\section{Contact}
205 Richard Pl 
Ithaca, NY
~
Cell:
607-379-0960
~
Email:-
at1777@rit.edu
andreitumbar
@gmail.com
%
%
\section{Programming
   Languages}
C, Python, Cython,
Java, C++ JavaScript,
CSS, HTML, Typescript
AJAX, \LaTeX{}
%
%
\section{Technologies}
\jobtitle{Linux admin} -- cgroups namespacing, SSL, SSH, libarchive, kernel, Xorg, nginx
\jobtitle{Database} -- PostgreSQL
\jobtitle{Webframeworks} -- Django, Google API
\jobtitle{Cloud-computing} -- Amazon AWS EC2
%
\end{aside}


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Work}{Experience}

\begin{entrylist}
%------------------------------------------------
\entry
  {2018, 2019}
  {Cornell University}
  {Ithaca, New York}
  {\jobtitle{Programmer}\\
  Implemented statistical model front-ends in Mathematica and Python. \\(letter of recommendation available upon request).}
\entry
  {Jun-2019}
  {Treman State Park}
  {Ithaca, New York}
  {\jobtitle{Maintenance}\\
Maintained Park facilities and trails. Worked independently supervising on other persons.
  }

\entry
  {Jun-2018}
  {Ithaca Streets and Facilities}
  {Ithaca, New York}
  {\jobtitle{Building maintenance assistant}\\
Assisted with basic maintenance work including plumbing, HVAC, fire alarms, electrical, carpentry work.

  }
%------------------------------------------------

%------------------------------------------------
%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\begin{entrylist}
%------------------------------------------------
\entry
{2019--now}
{BS candidate {\normalfont in Computer Engineering (3.91 GPA) -- May 2023} \\
\begin{itemize}%[label=$\bullet$, leftmargin=*]
	\item Computer Science II
	\item Digital System Design I
	\item Calculus I-IV, Uni-Phys I-II
	\item Discrete Math \& Linear Algebra
	\item Circuits I
\end{itemize}
}
{Rochester Institute of Technology}
{\vspace{-0.3cm}}

%------------------------------------------------
\entry
{2015--2019}
{Diploma {\normalfont Ithaca High School}}
{IHS}
{\vspace{-5.0cm}}
{}

%------------------------------------------------
\end{entrylist}



%----------------------------------------------------------------------------------------
%	OTHER QUALIFICATIONS SECTION
%----------------------------------------------------------------------------------------

\section{Projects}

\begin{entrylist}
%------------------------------------------------
\entry
{2014-now}
{AutoGentoo }
{github.com}
{A scalable Linux environment manager for creating optimized Gentoo Linux environments. Designed to bring higher performance to any platform (embedded or desktop) at low maintenance cost. TCP over TLS for cross domain management. Linux namespacing and cgroups for environment isolation. Django-based front-end \\ (\textbf{\href{https://autogentoo.org}{autogentoo.org}}).\\
\textbf{\href{https://github.com/AutoGentoo/AutoGentoo}{https://github.com/AutoGentoo/AutoGentoo}}
}

\entry
{2019-now}
{CPortage}
{github.com}
{A highly optimized rewrite of Gentoo's package manager. Optimized I/O and dynamic dependency calculations as well as a faster language parser. \\\textbf{\href{https://github.com/AutoGentoo/AutoGentoo/tree/develop/cportage}{https://github.com/AutoGentoo/AutoGentoo/tree/develop/cportage}}
}

\entry
{Jun-2019}
{Raspberry Pi Quadcopter }
{Ithaca High School}
{3D printed quad-copter with a Raspberry Pi control. Implemented PID control for closed-loop stabilization. \textbf{\href{https://github.com/Kronos3/Quadcopter}{https://github.com/Kronos3/Quadcopter}} }
{\vspace{-0.3cm}}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	Achievement  SECTION
%----------------------------------------------------------------------------------------
\pagebreak
\section{Achievements}

\begin{entrylist}
%------------------------------------------------
\entry
{}
{Technology Bowl 1\textsuperscript{st} place}
{2018 TSA national competition -- Atlanta Georgia}
{Technology Student Association team competition. Teams compete to test their knowledge across multiple STEM subjects (Computer Science, Biology, Chemistry, Physics, Engineering)}

\end{entrylist}
\begin{entrylist}

%------------------------------------------------
\entry
{}
{Website Design 5\textsuperscript{th} place}
{2018 TSA national competition -- Atlanta Georgia}
{Website front-end design as a team. Worked on CSS and Javascript frameworks as well as 3D graphics.}

%------------------------------------------------

\end{entrylist}
\begin{entrylist}

\entry
{}
{Engineering Dean's List}
{Rochester Institute of Technology}
{Maintained a GPA of \textbf{3.5} or higher.}

\end{entrylist}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{General}{Interests}

\vspace{-0.3cm}
\begin{entrylist}
%------------------------------------------------
\entry
{}
{Linux and Open-Source}
{}
{Love open-source and linux because of freedom, design, and customizability.}

\end{entrylist}\
\begin{entrylist}
%------------------------------------------------
\entry
{}
{C}
{}
{Networking, thread schedulers, grammar parsers, advanced data structures, tree recursion. Around 3+ years of experience.}
\end{entrylist}\
\begin{entrylist}
%------------------------------------------------
\entry
{}
{Python}
{}
{I/O scripts, complex string parsers, and polymorphic GUI design. Web frameworks like Django. Around 6+ years of experience.}

\end{entrylist}\
%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Skills}{}

\vspace{-0.2cm}

\begin{entrylist}
%------------------------------------------------
\entry
  {}
  {Time Management skills}
  {}
  {Able to keep up with an 18 credit semester and have time to work on personal projects.}
%------------------------------------------------
\entry
  {}
  {Programming Ability }
  {}
  {Advanced programming skills in C and Python. Profficient in Java and C++.}
  
  \entry
  {}
  {Quick Learning Capability}
  {}
  {Able to learn new APIs and programming languages with ease.}
  
  \entry
  {}
  {Teamwork Skills}
  {}
  {Competed in Engineering and Computer Science competitions at the national level very successfully in multiple teams.}

  
%------------------------------------------------
%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	Hobby SECTION
%----------------------------------------------------------------------------------------
\end{document}
\section{Hobbies}
  \vspace{-0.2cm}

\begin{entrylist}
%------------------------------------------------

%------------------------------------------------
\entry
  {}
  {Learn abut new Web technology }
  {}
  {\jobtitle{}\ Learn about the latest technology which helpful in company and Improve my
     programming Skills as well.}
  
  \entry
  {}
  {Find Out E-Commerce solution }
  {}
  {\jobtitle{}\ Find out Solution which arise in E-commerce platform on daily base 
  \begin{itemize}
    \item How to fast deliver the product. 
    \item Good Knowledge in CMS data Handling and 'HADOOP' Technology.
     
     
  \end{itemize}}
  \entry
  {}
  {Daily Morning Walk }
  {}
  {\jobtitle{}\ Go morning walk on daily base. }
  \entry
  {}
  {Read Technological Books }
  {}
  {\jobtitle{}\ Like DIGIT , Chip, Ftrack... }
  
%------------------------------------------------
%------------------------------------------------

\end{entrylist}


\end{document}